Still Missing a Cool Title

### 2006-05-31 talk/dls2006/paper.tex
A reference for partial evaluation.

In the context of the PyPy project, we are now exploring -- as we planned
from the start -- the possibility to produce a JIT as a graph
transformation aspect from the Python interpreter.  This idea is based
on the theoretical possibiliy to turn interpreters into compilers by
partial evaluation [PE].  In our approach, this is done by analysing
the forest of flow graphs built from the Python interpreter, which is a
well-suited input for this kind of techniques.  We can currently perform
binding-time analysis [BTA] on these graphs, again with abstract
interpretation techniques reusing the type inference engine.  The next
step is to transform the graphs -- following the binding-time annotations
- into a compiler; more precisely, in partial evalution terminology, a
generating extension.  We can currently do this on trivial examples.

>>>>

In the context of the PyPy project, we are now exploring -- as we planned
from the start -- the possibility to produce a JIT as a graph
transformation aspect from the Python interpreter.  This idea is based
on the theoretical possibiliy to turn interpreters into compilers by
partial evaluation\cite{Jones:1993:PartialEvaluation}.
In our approach, this is done by analysing
the forest of flow graphs built from the Python interpreter, which is a
well-suited input for this kind of techniques.  We can currently perform
binding-time analysis on these graphs, again with abstract
interpretation techniques reusing the type inference engine.  The next
step is to transform the graphs -- following the binding-time annotations
- into a compiler; more precisely, in partial evalution terminology, a
generating extension.  We can currently do this on trivial examples.
